Spectral-Spatial Hyper-spectral Image Classification Using Dual-Channel Capsule Networks

### 2020-03-11 paper/paper.tex
fixed some bugs

	Pavia University dataset, the Pavia Center dataset, the Salinas Valley dataset and the Salinas A dataset, which is
	a small subset of the Salinas Valley dataset.

@@

	Usually, a HSI dataset has labeled and unlabeled pixels.
	In our experiment we discarded those unlabeled pixels, only using the labeled pixels for training and testing.
	We divided the labeled pixels into 3 groups in our experiment: training data, testing data and validating data.
	We randomly selected 10\% of the total labeled pixels as training set, then we randomly selected 100 labeled pixels
	and the rest of the labeled pixels was used to validate the model.
	The training and validating dataset are shown in figure~\ref{trainMaps} and figure~\ref{testMaps}

@@

	\subsection{Environment}\label{subsec:environment}
	We trained and tested the model on a PC with 4 NVIDIA RTX 2080Ti(11GB) GPUs, dual Xeon 4210 Processor
	and 128GB of memory.
	The operating system is Ubuntu server 18.04 x64 LTS\@.
	We implement the model with Tensorflow 1.14.0 and the model is trained and tested on GPU\@.

	\subsection{Result and Analysis}\label{subsec:result-and-analysis}

@@

>>>>

	Pavia University(PU) dataset, the Pavia Center(PC) dataset, the Salinas Valley(SV) dataset and the Salinas A(SA)
	dataset, which is a small subset of the Salinas Valley dataset.

@@

	\subsection{Environment}\label{subsec:environment}
	We trained and tested the model on a PC with 4 NVIDIA RTX 2080Ti(11GB) GPUs, dual Xeon 4210 Processor
	and 128GB of memory.
	The operating system is Ubuntu server 18.04 x64 LTS with CUDA 10.1 and CUDNN 7.6.5.
	We implement the model with Tensorflow 1.14.0 and the model is trained and tested on GPU\@.

	\subsection{Experiment Setup}Usually, a HSI dataset has labeled and unlabeled pixels.
	In our experiment we discarded those unlabeled pixels, only using the labeled pixels for training and testing.
	We divided the labeled pixels into 3 groups in our experiment: training data, testing data and validating data.
	We randomly selected 10\% of the total labeled pixels as training set, then we randomly selected 100 labeled pixels
	and the rest of the labeled pixels was used to validate the model.
	The training and validating dataset are shown in figure~\ref{trainMaps} and figure~\ref{testMaps}

@@

	\subsection{Result and Analysis}\label{subsec:result-and-analysis}
	First of all, we listed the quantitative classification assessment using the PU, PC, SV and SA dataset considering
	SVM,
	1D CNN\cite{hu2015deep},
	2D CNN\cite{sharma2016hyperspectral},
	3D CNN\cite{hamida20183},
	3D FCN\cite{lee2016contextual},
	CNN-MRF\cite{cao2018hyperspectral},
	CapsNet and DCCN together.

@@

%Usually, a HSI dataset has labeled and unlabeled pixels.
%	In our experiment we discarded those unlabeled pixels, only using the labeled pixels for training and testing.
%	We divided the labeled pixels into 3 groups in our experiment: training data, testing data and validating data.
%	We randomly selected 10\% of the total labeled pixels as training set, then we randomly selected 100 labeled pixels
%	and the rest of the labeled pixels was used to validate the model.
%	The training and validating dataset are shown in figure~\ref{trainMaps} and figure~\ref{testMaps}
%
%	\begin{figure}
%		\begin{subfigure}
%			\includegraphics{pic/p5/pc/1/img/trainMap.eps}
%			\caption{}
%		\end{subfigure}
%		\begin{subfigure}
%			\includegraphics{pic/p5/pu/1/img/trainMap.eps}
%			\caption{}
%		\end{subfigure}
%		\begin{subfigure}
%			\includegraphics{pic/p5/sl/1/img/trainMap.eps}
%			\caption{}
%		\end{subfigure}
%		\begin{subfigure}
%			\includegraphics{pic/p5/sa/1/img/trainMap.eps}
%			\caption{}
%		\end{subfigure}
%		\caption{Training set for (a) Pavia Center, (b) Pavia University, (c) Salinas Valley and (d) Salinas A}
%		\label{trainMaps}
%	\end{figure}
%
%	\begin{figure}
%		\begin{subfigure}
%			\includegraphics{pic/p5/pc/1/img/testMap.eps}
%			\caption{}
%		\end{subfigure}
%		\begin{subfigure}
%			\includegraphics{pic/p5/pu/1/img/testMap.eps}
%			\caption{}
%		\end{subfigure}
%		\begin{subfigure}
%			\includegraphics{pic/p5/sl/1/img/testMap.eps}
%			\caption{}
%		\end{subfigure}
%		\begin{subfigure}
%			\includegraphics{pic/p5/sa/1/img/testMap.eps}
%			\caption{}
%		\end{subfigure}
%		\caption{Validating set for (a) Pavia Center, (b) Pavia University, (c) Salinas Valley and (d) Salinas A}
%		\label{testMaps}
%	\end{figure}
